---
title: "R Notebook"
output: html_notebook
---

Question 1

A collaborator sends you a file containing data for three years of average race finish times.

age_group,2015,2016,2017
20,3:46,3:22,3:50
30,3:50,3:43,4:43
40,4:39,3:49,4:51
50,4:48,4:59,5:01
Are these data considered “tidy” in R? Why or why not?

```{r}
# No. These data are not considered “tidy” because the variable “year” is stored in the header

# The year is a variable and should be stored as a column instead of across multiple columns in the header
```

Question 2

Below are four versions of the same dataset. Which one is in a tidy format?

```{r}
# state      abb region  population total
# Alabama     AL	South	4779736	  135

# In tidy format, each observation has its own row, and each variable has its own column
```

Question 3

Your file called “times.csv” has age groups and average race finish times for three years of marathons.

age_group,2015,2016,2017
20,3:46,3:22,3:50
30,3:50,3:43,4:43
40,4:39,3:49,4:51
50,4:48,4:59,5:01
You read in the data file using the following command.
    
d <- read_csv("times.csv")

```{r}
# tidy_data <- d %>%
# gather(year, time, `2015`:`2017`)

# This code will gather the years from 2015 to 2017 into a single column and create a single column called “time” that contains the time for each age group and each year
```

Question 4

You have a dataset on U.S. contagious diseases, but it is in the following wide format:

> head(dat_wide)
state year population HepatitisA Mumps Polio Rubella
Alabama 1990    4040587      86	   19    76    1
Alabama 1991    4066003      39	   14    65    0
Alabama 1992    4097169      35	   12    24    0
Alabama 1993    4133242      40	   22    67    0
Alabama 1994    4173361      72	   12    39    0
Alabama 1995    4216645      75     2    38    0
  
You want to transform this into a tidy dataset, with each row representing an observation of the incidence of each specific disease (as shown below):

> head(dat_tidy)
state   year  population  disease  count
Alabama 1990	4040587 HepatitisA	86
Alabama 1991	4066003 HepatitisA	39
Alabama 1992	4097169 HepatitisA	35
Alabama 1993	4133242 HepatitisA	40
Alabama 1994	4173361 HepatitisA	72
Alabama 1995	4216645 HepatitisA	75
  
Which of the following commands would achieve this transformation to tidy the data?

```{r}
# dat_tidy <- dat_wide %>%
# gather(key = disease, value = count, HepatitisA:Rubella)

# In this command, you properly specified that the “key” column will be called “disease”, the value of each entry will be called “count”, and that the columns HepatitisA through Rubella will all be included in the gather command
```

Question 5

You have successfully formatted marathon finish times into a tidy object called tidy_data. The first few lines are shown below.

age_group year   time
20        2015   03:46
30        2015   03:50
40        2015   04:39
50        2015   04:48
20        2016   03:22
Select the code that converts these data back to the wide format, where each year has a separate column

```{r}
# tidy_data %>% spread(year, time)

# This code tells the function to create new columns for each year and spread the time values over those cells
```

Question 6

You have the following dataset:

> head(dat)
state   abb region    	var   people
Alabama  AL  South population 4779736
Alabama  AL  South  	total 	  135
Alaska   AK   West population  710231
Alaska   AK   West  	total  	   19
Arizona  AZ   West population 6392017
Arizona  AZ   West  	total 	  232
  
You would like to transform it into a dataset where population and total are each their own column (shown below):

state      abb region population total
Alabama     AL  South	4779736   135
Alaska      AK   West 	 710231    19
Arizona     AZ   West	6392017   232
Arkansas    AR  South	2915918    93
California  CA   West  37253956  1257
Colorado    CO   West	5029196	   65

Which code would best accomplish this?

```{r}
# dat_tidy <- dat %>% spread(key = var, value = people)

# n this command, you properly specify that the column “var” will be used as the new column names, and that the column “people” should be spread into these two columns
```

Question 7

A collaborator sends you a file containing data for two years of average race finish times, "times.csv":

age_group,2015_time,2015_participants,2016_time,2016_participants
20,3:46,54,3:22,62
30,3:50,60,3:43,58
40,4:39,29,3:49,33
50,4:48,10,4:59,14
You read in the data file:

d <- read_csv("times.csv")

Which of the answers below best makes the data tidy?

```{r}
# tidy_data <- d %>%
# gather(key = “key”, value = “value”, -age_group) %>%
# separate(col = key, into = c(“year”, “variable_name”), sep = “_”) %>% 
# spread(key = variable_name, value = value)

# This column gathers the column names 2015_time, 2015_participants, 2016_time, and 2016_participants into one column called “key”, with the values for each stored in the column “value.” The key column is then separated into two columns, “year” and “variable_name”. The two entries for “variable_name”, time and participants, are then spread into their own columns
```

Question 8

You are in the process of tidying some data on heights, hand length, and wingspan for basketball players in the draft. Currently, you have the following:

> head(stats)
key               value
allen_height      75
allen_hand_length 8.25
allen_wingspan	  79.25
bamba_height      83.25
bamba_hand_length 9.75
bamba_wingspan    94
  
Select all of the correct commands below that would turn this data into a “tidy” format with columns "height", "hand_length" and "wingspan"

```{r}
# tidy_data <- stats %>%
# separate(col = key, into = c("player", "variable_name"), sep = "_", extra = "merge") %>% 
# spread(key = variable_name, value = value)

# This is an efficient way to separate the key column into two new columns, “player” and “variable_name”, while keeping the full variable names using the extra command
```

```{r}
library(tidyverse)
library(dslabs)
```

Question 9

Examine the built-in dataset co2. This dataset comes with base R, not dslabs - just type co2 to access the dataset.

Is co2 tidy? Why or why not?

```{r}
co2

# co2 is not tidy: to be tidy we would have to wrangle it to have three columns (year, month and value), and then each co2 observation would have a row

# These data are not tidy because month is a variable and should be stored as a column instead of across multiple columns in the header. There are also multiple observations per row, and each observation should be a different row
```

Question 10

Run the following command to define the co2_wide object:

co2_wide <- data.frame(matrix(co2, ncol = 12, byrow = TRUE)) %>% 
    setNames(1:12) %>%
    mutate(year = as.character(1959:1997))

Use the gather() function to make this dataset tidy. Call the column with the CO2 measurements co2 and call the month column month. Name the resulting object co2_tidy.

Which code would return the correct tidy format?

```{r}
co2_wide <- data.frame(matrix(co2, ncol = 12, byrow = TRUE)) %>% 
    setNames(1:12) %>%
    mutate(year = as.character(1959:1997))

co2_tidy <- gather(co2_wide,month,co2,-year)
head(co2_tidy, n=24)

# gather takes 4 arguments: (1) the data, (2) the name of the key column, (3) the name of the value column, and optionally (4) the names of any columns not to gather. We want to collect the months as the key and CO2 as the value while keeping the year column as-is
```
Question 11

Use co2_tidy to plot CO2 versus month with a different curve for each year:

co2_tidy %>% ggplot(aes(as.numeric(month), co2, color = year)) + geom_line()

What can be concluded from this plot?

```{r}
co2_tidy %>% ggplot(aes(as.numeric(month), co2, color = year)) + geom_line()co2_tidy %>% ggplot(aes(as.numeric(month), co2, color = year)) + geom_line()

# CO2 concentrations are highest around May and the yearly average increased from 1959 to 1997

# In every year, the highest CO2 level is around May. The line legend shows that earlier years had lower CO2 levels and that CO2 levels generally increase relative to the previous year. The most recent years have the highest CO2
```

Question 12

Load the admissions dataset from dslabs, which contains college admission information for men and women across six majors, and remove the applicants percentage column:

library(dslabs)
data(admissions)
dat <- admissions %>% select(-applicants)

Your goal is to get the data in the shape that has one row for each major, like this:

major  men   women
A      62    82		
B      63    68		
C      37    34		
D      33    35		
E      28    24		
F       6     7	

Which command could help you to wrangle the data into the desired format?

```{r}
data(admissions)
dat <- admissions %>% select(-applicants)

dat_tidy <- spread(dat,gender,admitted)

# spread takes 3 arguments: (1) the data frame, (2) the key to spread across columns, and (3) the value to put in individual cells of the table
```

Question 13

Now use the admissions dataset to create the object tmp, which has columns major, gender, key and value:

tmp <- gather(admissions, key, value, admitted:applicants)
tmp

Combine the key and gender and create a new column called column_name to get a variable with the following values: admitted_men, admitted_women, applicants_men and applicants_women. Save the new data as tmp2.

Which command could help you to wrangle the data into the desired format?

```{r}
tmp <- gather(admissions, key, value, admitted:applicants)
# tmp

tmp2 <- unite(tmp,column_name,key,gender, sep="_")
tmp3 <- unite(tmp, column_name, c(key, gender))
head(tmp2, n=15)
head(tmp3, n=15)
```

Question 14

Which function can reshape tmp2 to a table with six rows and five columns named major, admitted_men, admitted_women, applicants_men and applicants_women?

```{r}
tmp2 %>% spread(column_name,value)
```

