---
title: "R Notebook"
output: html_notebook
---

Question 1

You have created data frames tab1 and tab2 of state population and election data, similar to our module videos:

```{r}
library(tidyverse)
library(dslabs)
tab <- left_join(murders,results_us_election_2016, by="state")
tab1 <- slice(tab,1:3,8,9) %>% select(state,population)
tab2 <- slice(tab,1:3,5:7) %>% select(state,electoral_votes)
dat <- left_join(tab1, tab2, by = "state")

# 5 rows by 3 columns

# When we use a left_join command, all rows in the left-hand table (in this case, tab1) are retained in the final table, so we expect to have five rows. In addition, columns from both tables will be included in the final “dat” table so we expect to have three columns

```

Question 2

We are still using the tab1 and tab2 tables shown in question 1. What join command would create a new table “dat” with three rows and two columns?

```{r}
dat <- semi_join(tab1, tab2, by = "state")
dat

# The semi_join command takes tab1 and limits it to states that are also in tab2, without adding the additional columns in tab2. This gives us three rows (states in both tables) and two columns (state and population, the two columns in tab1)
```

Question 3

Which of the following are real differences between the join and bind functions?

```{r}
# Binding functions combine by position, while join functions match by variables.

# Joining functions can join datasets of different dimensions, but the bind functions must match on the appropriate dimension (either same row or column numbers)

# Bind functions can combine both vectors and dataframes, while join functions work for only for dataframes
```

Question 4

We have two simple tables, shown below, with columns x and y:

> df1
 x     y    
 a     a    
 b     a    

> df2
 x     y    
 a     a    
 a     b  

Which command would result in the following table?

> final
 x     y    
 b     a   

```{r}
# final <- setdiff(df1, df2)

# The setdiff() command returns rows in df1 but not df2, which matches our table final
```

Introduction to Questions 5-7
Install and load the Lahman library. This library contains a variety of datasets related to US professional baseball. We will use this library for the next few questions and will discuss it more extensively in the Regression course. For now, focus on wrangling the data rather than understanding the statistics.

The Batting data frame contains the offensive statistics for all baseball players over several seasons.  Filter this data frame to define top as the top 10 home run (HR) hitters in 2016:

```{r}
library(Lahman)
top <- Batting %>% 
  filter(yearID == 2016) %>%
  arrange(desc(HR)) %>%    # arrange by descending HR count
  slice(1:10)    # take entries 1-10
top %>% as_tibble()
```
Also Inspect the Master data frame, which has demographic information for all players:

```{r}
Master %>% as_tibble()
```
Question 5

Use the correct join or bind function to create a combined table of the names and statistics of the top 10 home run (HR) hitters for 2016. This table should have the player ID, first name, last name, and number of HR for the top 10 players. Name this data frame top_names.

Identify the join or bind that fills the blank in this code to create the correct table:

```{r}
top_names <- top %>% left_join(Master, by="playerID") %>%
    select(playerID, nameFirst, nameLast, HR)

top_names
```
Question 6

Inspect the Salaries data frame. Filter this data frame to the 2016 salaries, then use the correct bind join function to add a salary column to the top_names data frame from the previous question. Name the new data frame top_salary. Use this code framework:

```{r}
top_salary <- Salaries %>% filter(yearID == 2016) %>%
  right_join(top_names) %>%
  select(nameFirst, nameLast, teamID, HR, salary)

top_salary
```
Question 7

Inspect the AwardsPlayers table. Filter awards to include only the year 2016.

How many players from the top 10 home run hitters won at least one award in 2016?

```{r}
AwardsPlayers %>% filter(yearID==2016) %>%
  inner_join(top, by ="playerID") 

AwardsPlayers %>% filter(yearID==2016) %>%
  inner_join(top, by ="playerID") %>% distinct(playerID)

Awards_2016 <- AwardsPlayers %>% filter(yearID == 2016)
length(intersect(Awards_2016$playerID, top_names$playerID))
```
How many players won an award in 2016 but were not one of the top 10 home run hitters in 2016?

```{r}
AwardsPlayers %>% filter(yearID==2016) %>%
  anti_join(top, by="playerID") %>% distinct(playerID)

length(setdiff(Awards_2016$playerID, top_names$playerID))
```

