---
title: "R Notebook"
output: html_notebook
---

Question 1

Which of the following is NOT an application of string parsing?

```{r}
# Formatting numbers and characters so they can easily be displayed in deliverables like papers and presentations

# Formatting text and numbers for deliverables is not an application of string parsing. String parsing is used as part of the data wrangling process
```

Question 2

Which of the following commands would not give you an error in R?

```{r}
# cat(" LeBron James is 6’8\" ")

# This would correctly print out your string. Because the string is enclosed in double quotes, (“”), you must use an escape character before the inches symbol (“)
```

Question 3

Which of the following are advantages of the stringr package over string processing functions in base R? Select all that apply

```{r}
# Functions in stringr all start with “str_”, which makes them easy to look up using autocomplete

# Stringr functions work better with pipes

# The order of arguments is more consistent in stringr functions than in base R
```

Question 4

You have a data frame of monthly sales and profits in R:

> head(dat)
# A tibble: 5 x 3
Month     Sales     Profit 
<chr>     <chr>     <chr>  
January   $128,568  $16,234
February  $109,523  $12,876
March     $115,468  $17,920
April     $122,274  $15,825
May       $117,921  $15,437

```{r}
# dat %>% mutate_at(2:3, parse_number)

# dat %>% mutate_at(2:3, funs(str_replace_all(., c("\\$|,"), ""))) %>% mutate_at(2:3, as.numeric)
```

